Simulations of gravity-driven flow of binary liquids in microchannels

### 2011-01-06 Text/paper.tex
typo fix: our -> out

While there are many works which simulate the Bretherton problem by the boundary value approach
\cite{ingham-plates,heil-bretherton}, those methods are of limited applicability for problems
involving complex geometries, free interface motion, or for problems involving coalescence and/or
droplet breakup. The continuous interface models are more flexible for those kind of simulations.
However, if the interface is smeared our over several grid nodes, the question of
proper film resolution in comparison with the interface resolution arises.  This work is focused on
exploring the parameter range of the binary liquid lattice
Boltzmann method for correctly resolving the flow in a range of capillary numbers.

>>>>

While there are many works which simulate the Bretherton problem by the boundary value approach
\cite{ingham-plates,heil-bretherton}, those methods are of limited applicability for problems
involving complex geometries, free interface motion, or for problems involving coalescence and/or
droplet breakup. The continuous interface models are more flexible for those kind of simulations.
However, if the interface is smeared out over several grid nodes, the question of
proper film resolution in comparison with the interface resolution arises.  This work is focused on
exploring the parameter range of the binary liquid lattice
Boltzmann method for correctly resolving the flow in a range of capillary numbers.
